Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-21 WRITEUP/ms.tex
mainly rewording and add some scattered ideas to last sections

Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \aips to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry} %DONE
We obtain {\it HST} images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical (V$-$band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

@@

\begin{figure}[!htbp]
\centering
% [height=1in,width=5in]
\includegraphics[trim=0 5 0 15, clip, width=0.232\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 0, clip, width=0.22\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{
An overlay of the velocity-integrated \bco emission on the {\it HST} V$-$band (F555W)
image. The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295. Right: contours
are color-coded to represent the red and blue wings of the emission.
\label{fig:CO21mom}}
\end{figure}

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5). The spectra map covers an extent of $\sim$10"$\times$10"
centering on the pixel that corresponds to the lensing galaxy. The velocity
and flux density scales are denoted in the top right panel.
BLAH: DR would want the pixel coordinates replaced by arcsec offset from
center. \label{fig:spatialSpec}}
\end{figure*}

@@

\subsection{Origin of the \bco emission} \label{sec:origin} %DONE
Evidently, the CO emission is co-spatial with the lensed optical emission in
the background AGN host galaxy. The question is then whether the optically
faint companion also contributes to the CO flux and thus contains a
non-negligible amount of molecular gas.
Indeed, based on our lens model presented in \Sec{lensmodel}, we find it
highly likely that part of the CO emission originates from
the companion. We thus classify RXJ1131 as a ``wet-wet'' merger.
However, we cannot quantify this with a mass ratio given the
spatial resolution. This will be verified in future higher-resolution observations.
In the subsequent sections, we will interpret RXJ1131
assuming this classification (i.e. a ``wet-wet'' merger).

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.23\textwidth]{../Figures/F555W_ContPdBI.eps}
\hspace{-0.5em}
\includegraphics[width=0.235\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Left: an overlay of the 2\,mm continuum emission on the optical image.
Right: VLA 5\,GHz continuum emission is overlaid on the optical image.
Contours in both images start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the left and right panel, respectively.
The central crosses indicate the centroid of the foreground galaxy,
as detected in the optical image. The synthesis beams are shown in the bottom left corner of each panel.
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc and their centroids
coincide with the optical emission from the quasar.
We extract the flux densities for the arc and the core in \Tab{photometry}.
We find a spectral index of $\alpha$\,=\,0.024 for the foreground
galaxy and $\alpha$\,=\,0.345 for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{-\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

\subsection{Photometry} \label{sec:photometry} %DONE
We compile \mir to \fir broadband photometry from various
catalogs available on the NASA/IPAC Infrared Science
Archive (IRSA) in \Tab{photometry} with aperture corrections
when warranted. These data were obtained from
the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
Wide-field Infrared Survey Explorer (WISE; \citealt{Wright10a}),
{\it Infrared Astronomical Satellite} (IRAS; \citealt{Neugebauer84a}), and
the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
\spitzer.
We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
Spitzer Heritage Archive and perform aperture photometry on
the channel 1 image to extract flux density at 3.6\,$\mu$m
since it is not available from the IRSA archive.

The emission in the IRAC images is slightly extended. We thus use the
HST image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

@@

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec., which is
motivated by the astrometry uncertainties in the VLA image as well as
the uncertainties provided by previous SIE lens model (C06).
We initialize the Einstein Radius based on the model parameters reported by C06
and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2".

% Check with Shane
Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF). In each model, we employ
$\sim$100,000 samples as the initial ``burn-in'' stage to stabilize the Markov
chains (which we then discard). We use the final $\sim$5,000
samplings to determine the posterior probability distributions. Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
$\sim$2.4\,kpc away from the AGN host galaxy.

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=0.85\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{Each panel corresponds to a lens model of RXJ1131 performed over a
channel slice $\sim$100\,\kms of the \bco data. Top: channel maps of the
PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
The location of the foreground lensing galaxy is indicated by a black dot and
its critical curve is traced by the orange solid line. The locations and
morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses (see text in \Sec{caveat} for caveats).
The caustic curves are represented as cyan lines. The beam of the
PdBI observations is shown in the bottom right corner of each panel.
Bottom: residual images of the best-fit models, obtained by
taking the Fourier transform after subtracting the best-fit model from the
data in the $uv$-domain. Contours start
at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
where $n$ is a positive integer.
\label{fig:model}}
\end{figure*}

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
\input{table_magFactor}
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across {\it HST}
H-Band, V-band, and I-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO, where the red wing
of \bco is apparently much brighter than that in the blue wing, consistent
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).

\subsection{\bco Dynamical modeling} \label{sec:dynamics} %DONE
This section proceeds under the assumption that RXJ1131 is
a rotating disk (see previous sections).
Assuming the velocities of the respective lens models
correspond to solely the tangential component (i.e., $\theta$ = 0), we extract
a pseudo PV diagram along the major axis in \Fig{PV} by slicing across their
source plane positions. The best-fit major axis is along PA of 121\degr.

We attempt to characterize the molecular gas kinematics using an empirically motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rotation curve becomes flat.
We perform non-linear least square fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on Monte Carlo simulation
of 500 iterations, which we perturb the input parameters according to a random
Gaussian distribution of sigma corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
$R_{t}$\,=\,10.6\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
We note, however, that since emission is not detected beyond the flat regime
of the rotation curve, the asymptotic velocity is poorly constrained.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.

\begin{figure}[!Htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
\caption{PV slice along the major axis in the source plane at PA\,=\,121\degr.
Dashed line shows the best-fit rotation curve using an arctangent model.
DR may suggest include MC simulation fits, maybe I will do that later.
 \label{fig:PV}}
\end{figure}

We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is inequivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
Studies of the Tully-Fisher relation typically use V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$) as the rotation velocity ($V_{\rm max}$ in their
terminology), which corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3 kpc inferred from the C06 lens model (converted to
our cosmology), who use all {\it HST} H--, V--, and I--bands in their
modeling. If only V$-$band is used, the half-light radius is $\sim$4kpc \citep{Brewer08a}.
This discrepancy arises owning to the exclusion of the more diffused emission in the V-band
(\ie V-band is missing the diffused emission).
This indicates that the molecular gas may be ... (see \Sec{size}). DR: ok, let's discuss this.

@@

\subsection{SED modeling} \label{sec:SED}
We extrapolated a power-law to 24 \micron to decompose the flux
at 24 \micron in MIPS.
%
%We fit modified blackbody functions to
%to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt 
%BLAH (rest frame; Dunne et al. 2003).)
%We added blah\% calibration uncertainties on the PdBI data.
%
%We check convergence of our chains by requiring that the autocorrelation length for each model parameter is 
%several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
%The code treats the instrument response. 
%
%% upper limit using decomposed 24 um
%% lower limit using fit without 24 um, but do I still want to fit a power-law for this?
%The best-fit SEDs are shown in \Fig{SED} and the resulting parameters (inferred from the BLAH of the posterior PDF) are listed in \Tab{SED}.
%% parameter estimation problem
%For these parameter estimation problems using MCMC to sample,
%the full answer is the full joint posterior PDF.
%We here report the summary statistics (global mode (where min. chi),
%marginal mode (in log file),
%posterior median (instead of posterior means; need to compute) and the 1$\sigma$ confidence intervals in the marginal PDF) to reflect the PDF shape.

\subsection{ISM properties}
We correct for lensing magnification using the median among our models ($\mu_{\rm L}$=BLAH).
Assuming a Salpeter initial mass function, we find the SFR of blah using the \fir luminosity after corrected for lensing .
\subsection{Gas Mass}
\subsection{Source Extent} \label{sec:size}
Compared to HST:

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}
\subsection{Merger stage of RXJ1131-1231}

As discussion in previous sections, while we see evidence such as a symmetric velocity field in the source plane, double-horned profile, observed velocity
gradient, C06 model $n$=1 Sersic profile, which suggest that RXJ1131 is likely a rotating disc. Yet, this is insufficient to conclude a disk morphology. Additional characteristics such as peak velocity dispersion at the central region and a ``spider'' diagram are needed, which is commonly seen in local spirals.

\subsection{Implications}
gas fraction at this redshift. how does that relate to
the SFH, and the change in cosmic SFD is due to change in gas content.
SFE at this redshift, how does that relate to the SFH. probably a secondary effect to the drop in SFH

>>>>

Observations were carried out on 2008 December 29 under excellent weather
conditions in the A array configurations for a total of $\sim$7 hours on-source time. The C$-$band receivers were used with a continuum mode setup,
providing a bandwidth of 50 MHz in each sideband.
The nearby radio quasar 1130$-$149 was observed every 10 minutes for
pointing, amplitude, and phase calibration, 1331$-$305 was observed as the
primary flux calibrator, and 0319$+$415 was observed as the bandpass
calibrator, yielding $\sim$10\% calibration accuracy.
We use \ncode{AIPS} to calibrate the visibility data which
are then imaged and deconvolved using
the CLEAN algorithm using robust\,=\,0. This yields a synthesized clean
beam size of 0$\farcs$49 $\times$ 0\farcs35 (PA\,=\,0\farcs18) and a final
rms noise of $\sigma$ = 13 $\mu$Jy beam\pmOne.

\section{HST astrometry} %DONE
We obtain {\it HST} images from the Hubble Legacy Archive with
a goal to understand the origins of the emission detected
in our mm observations. We adopt the VLA 5\,GHz map of $\sim$0\farcs5
resolution as the reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. Such astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR, phase
errors, and beam size.

@@

\begin{figure}[!htbp]
\includegraphics[trim=3 5 0 15, clip, width=0.242\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=3 5 0 0, clip, width=0.23\textwidth]{../Figures/F555W_REDBLUE.eps}
\caption{Left: an overlay of the velocity-integrated \bco emission on the {\it HST} $V$--band (F555W)
image. Right: contours are color-coded to represent the red and blue wings of the emission.
The contours start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne. The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
\label{fig:CO21mom}}
\end{figure}

@@

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.85\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5). The spectra map covers an extent of $\sim$10"$\times$10"
centering on the pixel that corresponds to the lensing galaxy. The velocity
and flux density scales are denoted in the top right panel.
BLAH: DR would want the pixel coordinates replaced by arcsec offset from
center. \label{fig:spatialSpec}}
\end{figure*}

@@

\subsection{Origin of the \bco Emission} \label{sec:origin} %DONE
Evidently, the CO emission is co-spatial with the lensed optical emission in
the background AGN host galaxy.
The question is then whether the optically
faint companion also contributes to the CO flux and thus contains a
non-negligible amount of molecular gas.
Indeed, based on our lens model presented in \Sec{lensmodel}, we find it
highly likely that part of the CO emission originates from
the companion. We thus classify RXJ1131 as a ``wet-wet'' merger.
However, we cannot quantify this with a mass ratio given the
spatial resolution, nor can we rule out the possibility that
the ``companion'' is instead a gas component/tidal feature ripped out
from previous interaction. In the subsequent sections, we will interpret
the this additional source component as gas emission
in a nearby galaxy (i.e. a ``wet-wet'' merger), as suggested by previous studies of RXJ1131.

@@

\begin{figure}[!htbp]
%\centering
\includegraphics[trim=12 27 0 0, clip, width=0.45\textwidth]{../Figures/F555W_ContPdBI.eps}
\includegraphics[trim=10 5 0 0, clip, width=0.475\textwidth]{../Figures/F555W_ContVLA.eps}
\caption{Top: an overlay of the 2\,mm continuum emission on the optical image.
Bottom: VLA 5\,GHz continuum emission is overlaid on the optical image.
Contours in both images start and increment at steps of
$\pm$3$\sigma$, where $\sigma_{\rm 2mm}$\,=\,0.082 mJy beam\pmOne and
$\sigma_{\rm 5GHz}$\,=\,13 $\mu$Jy beam\pmOne in the left and right panel, respectively.
The central crosses indicate the centroid of the foreground galaxy,
as detected in the optical image. The synthesis beams are shown in the bottom left corner of each panel.
\label{fig:cont}}\vspace{0.51em}
\end{figure}

The VLA C-band continuum image in \Fig{cont} shows resolved emission from the
jets and core of the foreground elliptical galaxy
as well as emission toward the background quasar.
Multiple peaks are seen along the arc and their centroids
coincide with the optical emission from the quasar.
We extract the flux densities for the arc and the core in \Tab{photometry}.
We find a spectral index of $\alpha$\,=\,$-$0.024 for the foreground
galaxy and $\alpha$\,=\,$-$0.345 for the background galaxy by fitting a
power-law (S$_\nu \propto \nu^{\alpha}$) to the continuum emission at
5\,GHz and 2\,mm.

\subsection{Photometry} \label{sec:photometry} %DONE
We compile \mir to \fir broadband photometry from various
catalogs available on the NASA/IPAC Infrared Science
Archive (IRSA) in \Tab{photometry} with aperture corrections
when warranted. These data were obtained from
the Two Micron All Sky Survey (2MASS; \citealt{Skrutskie06a}),
Wide-field Infrared Survey Explorer ({\it WISE}; \citealt{Wright10a}),
{\it Infrared Astronomical Satellite}
({\it IRAS};\citealt{Neugebauer84a}), and
the Multiband Imaging Photometer (MIPS; \citealt{Rieke04a}) and
Mid-infrared Infrared Array Camera (IRAC; \citealt{Fazio04a}) on
\spitzer.
We retrieve PBCD (level 2) {\it Spitzer}/IRAC images from the
Spitzer Heritage Archive and perform aperture photometry on
the channel 1 image to extract flux density at 3.6\,$\mu$m
since it is not available from the IRSA archive.

The emission in the IRAC images is slightly extended. We thus use the
{\it HST} image ($\sim$0\farcs07 resolution) to determine
origins of their centroids, all of which are found to be
centered at the position corresponding to the lensed emission from the
background galaxy. To recover the diffuse background emission, we subtract a
point source model centered on the lensing galaxy, using the average
FWHM found by fitting a Gaussian profile to several field stars
with the \ncode{imexam} routine of IRAF.
We perform aperture photometry on the residual image
to obtain decomposed flux measurements from the background galaxy.
The photometries for the foreground galaxy are then obtained
by subtracting the fluxes decomposed for the background source
from the observed total flux. The resulting photometry in
\Tab{photometry} are obtained after performing aperture correction
described in the IRAC Instrument Handbook\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/iracinstrumenthandbook/} to
correct for the fact that the IRAC imaging was calibrated
using a 12" aperture, which is bigger than the aperture (5\farcs8) we used to
perform aperture photometry. This step was taken to provide
constraints on the Wien tail beyond the dust peak of the
spectral energy distribution (SED) of RXJ1131.
Details of the SED modeling is presented in \Sec{SED}.

@@

The lens mass distribution is modeled using a singular isothermal
ellipsoid (SIE) profile, which is described by five free parameters: the
positional offset in R.A. and Dec. relative to an arbitrary chosen
fixed coordinate in the image, the Einstein Radius, the axial ratio, and the
position angle. We use the VLA radio continuum emission toward
the foreground galaxy to initialize the positional offset. We impose a
uniform prior $\pm$0\farcs05 in both $\Delta$R.A. and $\Delta$Dec.,
motivated by the astrometry uncertainties in the VLA image as well as
the uncertainties provided by previous SIE lens model (C06).
We initialize the Einstein Radius based on the model parameters reported by C06
and impose a uniform prior using $\pm$3$\sigma$ of their uncertainties.
The sources are modeled using elliptical Gaussian profiles, which are
parameterized by six free parameters: the positional offset in R.A.
and Dec. relative to the lens, the intrinsic flux density, the effective
radius, the axial ratio, and the position angle. The position of each source
is allowed to vary between $\pm$1\farcs5 (i.e., within the Einstein Radius)
and the effective radius is allowed to vary from 0\farcs01$-$2".

% Check with Shane
{\bf NEEDS EDIT}
Our code uses an Markov Chain Monte Carlo (MCMC) approach to sample the
posterior probability distribution function (PDF).
In each model, we require the target acceptance rate of $\sim$0.25$-$0.5
and check for chain convergence by inspecting the trace plots
AND BLAH to verify we can samples beyond an autocorrelation time.
We employ $\sim$50,000 samples as the initial ``burn-in'' stage
to stabilize the Markov chains (which we then discard).
We then use the final $\sim$5,000 steps, sampled by 128 walkers.
Here, we
identify the best-fit model and the quoted uncertainties using the
median and the 68\% confidence intervals in the marginal PDFs.
\input{table_medianLens}

@@

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting dusty galaxy.
Spatially, the red velocity component of the CO also coincides with this
component F. While we cannot quantify the type of
merger (major v.s. minor) with a mass ratio given the
spatial resolution, the symmetric velocity gradient may lean support
towards a minor merger.

@@

\begin{figure*}[tbph]
%\centering
\includegraphics[width=1.0\textwidth]{../Figures/PostageStampModel.eps}
\includegraphics[width=1.0\textwidth]{../Figures/PostageStampResiduals.eps}
\caption{Each panel corresponds to a lens model of RXJ1131 performed over a
channel slice $\sim$100\,\kms of the \bco data. Top: channel maps of the
PdBI \bco emission (red) overlaid on our best-fit lens models (grayscale).
The location of the foreground lensing galaxy is indicated by a black dot and
its critical curve is traced by the orange solid line. The locations and
morphologies (half-light radii) of the reconstructed sources are
represented by magenta ellipses (see text in \Sec{caveat} for caveats).
The caustic curves are represented as cyan lines. The beam of the
PdBI observations is shown in the bottom right corner of each panel.
Bottom: residual images of the best-fit models, obtained by
taking the Fourier transform after subtracting the best-fit model from the
data in the $uv$-domain. Contours start
at $\pm$3$\sigma$ and increment at steps of 3$\times$2$^n\sigma$,
where $n$ is a positive integer.
\label{fig:model}}
\end{figure*}

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
\input{table_magFactor}
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across {\it HST}
$H$-, $V$-, and $I$-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO, where the redshifted
emission is apparently much brighter than that in the
blueshifted emission, consistent
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO ranges from 8.7 to 3.1 (\Tab{model}).

\subsection{\bco Dynamical modeling} \label{sec:dynamics} %DONE
This section proceeds under the assumption that RXJ1131 is
a rotating disk (see previous sections).
Assuming the velocities of the respective channels used in
lens modeling correspond to solely the tangential component of the
true velocity vector (i.e., along the major axis), we extract
a one dimensional PV diagram in \Fig{PV}
by slicing across their source plane positions (PA: 121\degr).

We attempt to characterize the molecular gas kinematics using an empirically motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rotation curve becomes flat.
We perform non-linear least square fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on Monte Carlo simulation
of 500 iterations, where the input parameters are perturbed
according to random Gaussian distributions of sigmas
corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,975\,$\pm$\,387 \kms,
$R_{t}$\,=\,10.6\,$\pm$\,5.7\,kpc, and $V_0$\,=\,28\,$\pm$\,40 \kms.
We note, however, that since emission is not detected beyond the flat regime
of the rotation curve, the asymptotic velocity is poorly constrained and
the ``turnover'' radius is at most a lower limit.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and 0.027 between $V_{a}$ and $V_0$.

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.455\textwidth]{../Figures/bestfit_PV.eps}
\caption{PV slice along the major axis in the source plane at PA\,=\,121\degr.
Dashed line shows the best-fit rotation curve using an arctangent model.
The vertical error bars show the channel width for
each model and the horizontal error bars are the
1$\sigma$ uncertainties on the source plane positions.
DR may suggest include MC simulation fits, maybe I will do that later.
 \label{fig:PV}}
\end{figure}

We note that the asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is inequivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the C06 lens model (converted to
our cosmology) over the {\it HST} $I$-band image.
We note that the source plane half-light radius varies substantially with
wavelength: $R_e$ $\sim$\,4kpc and $\sim$7\,kpc based on models over
$V$-band \citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces recent massive \SF.
% On the other hand, $I$-band traces the more evolved stellar population.
This indicates that the molecular gas may be ....
DR: ok, let's discuss this.

@@

\subsection{SED modeling} \label{sec:SED}
By fitting a power-law spectrum $S_\nu \propto \nu^\alpha$ to the decomposed
IRAC photometry. We find a spectral index of $\alpha\sim-$1.9 and
$\alpha\sim-$0.85 for the lensing galaxy and RXJ1131, respectively.
This is consistent with the mean spectral slope of optical quasars
(optically-selected) ($\alpha\sim-$1, Elvis et al. 1994;
Neugebauer et al. 1979).
For comparison, broad-line AGN from the AGN and Galaxy
Evolution Survey (AGES, C. S. Kochanek et al., in prep) have 3.6$-$8 \micron slopes of $\alpha$ = $-$1.07$\pm$0.53 (Stern et al. 2005).

We extrapolated a power-law to 24 \micron to decompose the flux
at 24 \micron in MIPS.
Since the contribution from AGN is not taken into account in SBURT, it is expected that the SEDs of AGN candidates show an excess in the MIR, owing to hot dust around the central massive black hole,
NIR not corrected for extinction.

We fit SED models to the photometry of dust emission in RXJ1131-1231 with a power-law attached to the blue side.
We include the IRAS 60\micron and 100\micron upper limits to constrain the dust peak.
We also fit SED models including the decomposed 24.0\micron data (see \Sec{photometry})

Spitzer mid-IR spectroscopy of local ULIRGs will indicate the appropriate luminosity fraction that needs to be assigned to the AGN for ULIRGs before and after nuclear coalescence.
ULIRG Lir
Our SED model find a rest-frame characteristic dust temperature of BLAH (cf. 60-70K in the cores of local ULIRGs/SB; Pauzzo+11, Rangwala+10)

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.8\textwidth]{../Figures/FullSED.eps}
\caption{
WISE flux is higher than the IRAC data, probably just due to smaller aperture used in IRAC.
Spitzer IRAC: Aperture flux in 5\farcs diameter with aperture correction applied.
Spitzer/MIPS: PSF fit flux, as source size <
native PSF FWHM of 6".
Might want to add NVSS constraints.
 \label{fig:SED}}
\end{figure*}

We fit modified blackbody functions to
to constrain the dust temperature, \fir (rest-frame 42.5-122.5 \micron) luminosity, dust mass (For the mass absorption coefficient we adopt
BLAH (rest frame; Dunne et al. 2003).)
We added blah\% calibration uncertainties on the PdBI data.

We check convergence of our chains by requiring that the autocorrelation length for each model parameter is
several times less than the number of steps taken during an initial burn-in stage (which are then discarded).
The code treats the instrument response.
flux using the set of photometric filters used to obtain the observations.
